%&biglatex
% Latex 2e document, tac article style, 47 pp, Xy-pic ver 3.7, MiKTeX version 2.1
\documentclass{tac}
\usepackage{rotating}
\usepackage{graphics}
\usepackage[all]{xy}
\xyoption{v2}
\xyoption{knot}


\author {S. Forcey and J. Siehler}

\thanks{Thanks to {\Xy-pic} for the diagrams. }

\address{Department of Mathematics\\
     Virginia Tech\\
     460 McBryde Hall\\
     Blacksburg, VA 24060 \\
     USA\\
}


\title {Combinatoric n-fold categories and n-fold operads}


\copyrightyear{2003}

\keywords{operads, iterated monoidal categories}
\amsclass{18D10; 18D20}

\eaddress{sforcey@math.vt.edu}


%NOTE:  author macros  BEGIN here
%       (they are all actually used in the article!!)

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

\newcommand{\MySection}[1]
{\section{ #1}}

\newcommand{\bcal}[1]{\mbox{\boldmath${\cal {#1}}$}}
\mathrmdef{Hom}
\mathrmdef{sort}

% author macros END here

\begin{document}
\SloppyCurves{

\maketitle
\begin{abstract}
 Operads were originally defined as ${\cal V}$-operads, that is, enriched in a symmetric monoidal category ${\cal V}.$
 The symmetry in ${\cal V}$ is required in order
 to describe the associativity axiom the operads must obey, as well as the associativity that
 must hold in the action of an operad on one of its algebras. A sequence of categorical types that 
 filter the category of monoidal categories and monoidal functors is given by Balteanu, Fiedorowicz, Schwanzl and Vogt in 
 \cite{Balt}. The subcategories of {\bf MonCat} are called $n$-fold monoidal categories. A $k$--fold monoidal category
 is $n$-fold monoidal for all  $n\le k$, and a symmetric monoidal category is $n$-fold monoidal for all $n$.
 We begin with definitions and simple examples of iterated monoidal categories.  
 Then we generalize the definition of operad by defining n-fold operads and their algebras in an iterated monoidal category.
 We discuss examples of these that live in the previously described categories. Finally we describe 
 the $n-2$-fold monoidal category of $n$-fold ${\cal V}$-operads. 
 
 
 
 A possible aside: n-fold operads as certain monoids.
 We may also want to compare n-fold operads with globular operads as
 defined by Michael Batanin in "Monoidal Globular Categories As a Natural Environment
 for the Theory of Weak n-Categories." (Advances in Math 136, 39-103, 1998).
 An MGC is very close to being n-fold monoidal. Interchanges are isos. 
 Globular ("higher order") operads live in these, and take all sorts of pasting diagrams
 as input types, as opposed to just a string as in the case of normal operads (which can be
seen as parameterizing a collection of n-ary operations for natural numbers n).
 
 \end{abstract}

  %{intro2}
      \clearpage
                  \tableofcontents 
      \clearpage
      %\clearpage
                %\newpage
            \MySection{Introduction}

    \clearpage
          \newpage
        \MySection{$k$-fold monoidal categories}
      This sort of category was
    developed and defined in \cite{Balt}. The authors describe its structure as arising from its description
    as a monoid in the
        category of $(k-1)$-fold monoidal categories. Here is that definition altered only slightly 
    to make visible the coherent associators as in \cite{forcey1}. In that paper I describe its structure as 
    arising from its description
    as a tensor object in the
        category of $(k-1)$-fold monoidal categories.
        
\begin{definition}\label{iterated} An $n${\it -fold monoidal category} is a category ${\cal V}$
          with the following structure. 
          \begin{enumerate}
          \item There are $n$ distinct multiplications
          $$\otimes_1,\otimes_2,\dots, \otimes_n:{\cal V}\times{\cal V}\to{\cal V}$$
          for each of which the associativity pentagon commutes
          
          \noindent
  		          \begin{center}
  	          \resizebox{4.5in}{!}{
          $$
          \xymatrix@R=45pt@C=-35pt{
          &((U\otimes_i V)\otimes_i W)\otimes_i X \text{ }\text{ }
          \ar[rr]^{ \alpha^{i}_{UVW}\otimes_i 1_{X}}
          \ar[dl]^{ \alpha^{i}_{(U\otimes_i V)WX}}
          &\text{ }\text{ }\text{ }\text{ }\text{ }&\text{ }\text{ }(U\otimes_i (V\otimes_i W))\otimes_i X
          \ar[dr]^{ \alpha^{i}_{U(V\otimes_i W)X}}&\\
          (U\otimes_i V)\otimes_i (W\otimes_i X)
          \ar[drr]^{ \alpha^{i}_{UV(W\otimes_i X)}}
          &&&&U\otimes_i ((V\otimes_i W)\otimes_i X)
          \ar[dll]^{ 1_{U}\otimes_i \alpha^{i}_{VWX}}
          \\&&U\otimes_i (V\otimes_i (W\otimes_i X))&&&
          }
          $$
          }
  		                    \end{center}
  	                    
          
          ${\cal V}$ has an object $I$ which is a strict unit
          for all the multiplications.
          \item For each pair $(i,j)$ such that $1\le i<j\le n$ there is a natural
          transformation
          $$\eta^{ij}_{ABCD}: (A\otimes_j B)\otimes_i(C\otimes_j D)\to
          (A\otimes_i C)\otimes_j(B\otimes_i D).$$
          \end{enumerate}
          These natural transformations $\eta^{ij}$ are subject to the following conditions:
          \begin{enumerate}
          \item[(a)] Internal unit condition: 
          $\eta^{ij}_{ABII}=\eta^{ij}_{IIAB}=1_{A\otimes_j B}$
          \item[(b)] External unit condition:
          $\eta^{ij}_{AIBI}=\eta^{ij}_{IAIB}=1_{A\otimes_i B}$
          \item[(c)] Internal associativity condition: The following diagram commutes
          
          \noindent
	  	            	          \begin{center}
	      	          \resizebox{5in}{!}{
	     $$
            \diagram
            ((U\otimes_j V)\otimes_i (W\otimes_j X))\otimes_i (Y\otimes_j Z)
            \xto[rrr]^{\eta^{ij}_{UVWX}\otimes_i 1_{Y\otimes_j Z}}
            \ar[d]^{\alpha^i}
            &&&\bigl((U\otimes_i W)\otimes_j(V\otimes_i X)\bigr)\otimes_i (Y\otimes_j Z)
            \dto^{\eta^{ij}_{(U\otimes_i W)(V\otimes_i X)YZ}}\\
            (U\otimes_j V)\otimes_i ((W\otimes_j X)\otimes_i (Y\otimes_j Z))
            \dto^{1_{U\otimes_j V}\otimes_i \eta^{ij}_{WXYZ}}
            &&&((U\otimes_i W)\otimes_i Y)\otimes_j((V\otimes_i X)\otimes_i Z)
            \ar[d]^{\alpha^i \otimes_j \alpha^i}
            \\
            (U\otimes_j V)\otimes_i \bigl((W\otimes_i Y)\otimes_j(X\otimes_i Z)\bigr)
            \xto[rrr]^{\eta^{ij}_{UV(W\otimes_i Y)(X\otimes_i Z)}}
            &&& (U\otimes_i (W\otimes_i Y))\otimes_j(V\otimes_i (X\otimes_i Z))
            \enddiagram
            $$
           }
	            	                    \end{center}
  
           \item[(d)] External associativity condition: The following diagram commutes
            
            \noindent
  	            	          \begin{center}
      	          \resizebox{5in}{!}{ 
             $$
             \diagram
            ((U\otimes_j V)\otimes_j W)\otimes_i ((X\otimes_j Y)\otimes_j Z)
            \xto[rrr]^{\eta^{ij}_{(U\otimes_j V)W(X\otimes_j Y)Z}}
            \ar[d]^{\alpha^j \otimes_i \alpha^j}
            &&& \bigl((U\otimes_j V)\otimes_i (X\otimes_j Y)\bigr)\otimes_j(W\otimes_i Z)
            \dto^{\eta^{ij}_{UVXY}\otimes_j 1_{W\otimes_i Z}}\\
            (U\otimes_j (V\otimes_j W))\otimes_i (X\otimes_j (Y\otimes_j Z))
            \dto^{\eta^{ij}_{U(V\otimes_j W)X(Y\otimes_j Z)}}
            &&&((U\otimes_i X)\otimes_j(V\otimes_i Y))\otimes_j(W\otimes_i Z)
            \ar[d]^{\alpha^j}
            \\
            (U\otimes_i X)\otimes_j\bigl((V\otimes_j W)\otimes_i (Y\otimes_j Z)\bigr)
            \xto[rrr]^{1_{U\otimes_i X}\otimes_j\eta^{ij}_{VWYZ}}
            &&& (U\otimes_i X)\otimes_j((V\otimes_i Y)\otimes_j(W\otimes_i Z))
            \enddiagram
            $$
          }
	           	                    \end{center}
   
          \item[(e)] Finally it is required  for each triple $(i,j,k)$ satisfying
          $1\le i<j<k\le n$ that
          the giant hexagonal interchange diagram commutes.
         \end{enumerate}
          
          \noindent
  		          \begin{center}
  	          \resizebox{6in}{!}{
          $$
          \xymatrix@C=-118pt{
          &((A\otimes_k A')\otimes_j (B\otimes_k B'))\otimes_i((C\otimes_k C')\otimes_j (D\otimes_k D'))
          \ar[ddl]|{\eta^{jk}_{AA'BB'}\otimes_i \eta^{jk}_{CC'DD'}}
          \ar[ddr]|{\eta^{ij}_{(A\otimes_k A')(B\otimes_k B')(C\otimes_k C')(D\otimes_k D')}}
          \\\\
          ((A\otimes_j B)\otimes_k (A'\otimes_j B'))\otimes_i((C\otimes_j D)\otimes_k (C'\otimes_j D'))
          \ar[dd]|{\eta^{ik}_{(A\otimes_j B)(A'\otimes_j B')(C\otimes_j D)(C'\otimes_j D')}}
          &&((A\otimes_k A')\otimes_i (C\otimes_k C'))\otimes_j((B\otimes_k B')\otimes_i (D\otimes_k D'))
          \ar[dd]|{\eta^{ik}_{AA'CC'}\otimes_j \eta^{ik}_{BB'DD'}}
          \\\\
          ((A\otimes_j B)\otimes_i (C\otimes_j D))\otimes_k((A'\otimes_j B')\otimes_i (C'\otimes_j D'))
          \ar[ddr]|{\eta^{ij}_{ABCD}\otimes_k \eta^{ij}_{A'B'C'D'}}
          &&((A\otimes_i C)\otimes_k (A'\otimes_i C'))\otimes_j((B\otimes_i D)\otimes_k (B'\otimes_i D'))
          \ar[ddl]|{\eta^{jk}_{(A\otimes_i C)(A'\otimes_i C')(B\otimes_i D)(B'\otimes_i D')}}
          \\\\
          &((A\otimes_i C)\otimes_j (B\otimes_i D))\otimes_k((A'\otimes_i C')\otimes_j (B'\otimes_i D'))
          }
          $$
          }
  		                    \end{center}
  	                    
          
          
        \end{definition}
  
     
     The authors of \cite{Balt} remark that a symmetric monoidal category is $n$-fold monoidal for all $n$.
     This they demonstrate by letting
        $$\otimes_1=\otimes_2=\dots=\otimes_n=\otimes$$
        and defining (associators added by myself)
        $$\eta^{ij}_{ABCD}=\alpha^{-1}\circ (1_A\otimes \alpha)\circ (1_A\otimes (c_{BC}\otimes 1_D))\circ (1_A\otimes \alpha^{-1})\circ \alpha$$
        for all $i<j$. Here $c_{BC}: B\otimes C \to C\otimes B$ is the symmetry natural transformation.

\newpage   
\MySection{Examples of iterated monoidal categories} 
\begin{enumerate}
\item
We start with an example of a monoidal category. Given a totally ordered set $G$ with a smallest element $e \in G$, 
then we have an ordered semigroup structure where the semigroup product is max and the 2-sided unit is the
least element $e$. The elements of $G$ make up the objects of a strict monoidal category whose morphisms are
given by the ordering; there is only an arrow $a \to b$ if $a\le b.$ The ordered semigroup structure implies
the monoidal structure on morphisms, since if $a\le b$ and $a'\le b'$ 
 then $\max(a,a')\le\max(b,b').$ The category will also be denoted $G.$ 
If $G$ is such a set then by Seq($G$) we denote the infinite sequences $X_n$ of elements of $G$ for which
there exists a natural number $l(X)$ such that $k> l(X)$ implies $X_k = e$ and $X_{l(X)}\ne e.$ 
Under lexicographic ordering Seq($G$) is
in turn a totally ordered set with a least element. The latter is the sequence 0 where $0_n = e$ for all $n.$
We let $l(0) = 0.$
The lexicographic order
means that $A \le B$ if either $A_k = B_k$ for all $k$ or there is a natural number $n=n_{AB}$ such that 
$A_k = B_k$ for all $k < n$, and such that $A_{n} < B_{n}.$ 

The ordering is easily shown to be reflexive, transitive, and antisymmetric. See for instance \cite{Schrod}
where the case of lexicographic ordering of $n$-tuples of natural numbers is dicussed. In our case we will need
to modify the proof by always making comparisons of $\max(l(A),l(B))$-tuples. 

As a category Seq($G$) is 2-fold monoidal since 
there are two possible products, max using the lexicographic order: $A\otimes_1 B = \max(A,B),$ 
and the piecewise max: $(A \otimes_2 B)_n = \max(A_n, B_n).$ The latter is  more generally described as
the piecewise application of the ordered semigroup product from $G.$ Such a piecewise application
will always be in turn an ordered
semigroup product since $A_i \le B_i$ and $C_i \le D_i$
implies that $A_iC_i \le B_iD_i$. Seq($G$) is thus an example of 
a $2$-fold monoidal category that is formed from any totally ordered semigroup . 
\begin{theorem}\label{semi}
Given a totally ordered semigroup $\{H\le\}$
such that the
identity element $0 \in H$ is less than every other element then 
we have a 2-fold monoidal category with 
objects are elements of $H.$ 
\end{theorem}
{\bf Proof}: Morphisms
are again given by the ordering. The products are given by
 $\max$ and the semigroup operation: $a\otimes_1b = \max(a,b)$ and $a\otimes_2b = ab$. 
 The shared two-sided unit for these products is 
 the identity element $0.$ The products are both strictly associative and functorial since if $a\le b$ and $a'\le b'$ 
 then $aa'\le bb'$ and $\max(a,a')\le\max(b,b').$
 The interchange natural tranformations exist since $\max(ab,cd)\le\max(a,c)\max(b,d).$ This last theorem is easily seen by checking the four
 possible cases: $\{c\le a, d\le b\};~~\{c\le a, b\le d\};~~\{a\le c, d\le b\};~~\{a\le c, b\le d\};$ or by the 
 quick argument that
 
 $
   a \le max(a,c) \text{ and } b \le max(b,d)  \text{ so } $
   
              $  ab \le max(a,c)max(b,d)   \text{ and similarly } $
                
              $  cd \le max(a,c)max(b,d).
$
 
 The internal and external unit and associativity conditions of Definition~\ref{iterated} are all satisfied due to the
 fact that there is only one morphism between two objects. 
 
 Besides Seq($G$) examples
 of such semigroups are the nonnegative integers under addition
 and the braids on $n$ strands with only right-handed crossings. There is also an alternative
 to the piecewise max on the objects of Seq($G$), concatenation of sequences. This is a valid semigroup
 operation and thus monoidal product since it clearly preserves the lexicographic order. A non-example,
 however, is revealed in an attempt to have both the piecewise max and the concatenation at once in
 a 3-fold monoidal category along with lexicographic max. The required interchange morphisms between
 concatenation and piecewise max do not exist. Further examples are found in the papers on
 semirings and idempotent mathematics, such as \cite{LitSob} and its references as well as on
 the related concept of tropical mathematics, such as \cite{Sturm} and its references. Semirings in these
 fields usually require some 
 translation to yield 2-fold monoidal categories since they typically have a zero and a unity, $0 \ne 1.$ 
 
 The step taken to create Seq($G$) can be iterated to create $n$-fold monoidal categories for all $n.$ 
 In general, if we have a $k$-fold monoidal category $C$ with morphisms ordering of objects and the
common unit and smallest element $I$ such that $A\in C \Rightarrow I\le A$ then:

\begin{tabular}{ll}
1.&we can form a $(k+1)$-fold monoidal category $\hat{C}$ with $\hat{\otimes}_1 = \max$ and $\hat{\otimes}_i = \otimes_{i-1}$\\
2.&we can form the $(k+2)$-fold monoidal Seq$(C)$ with objects ordered\\ 
&lexicographically.
\end{tabular}
The new $\otimes_1$ is the maximum of sequences with
respect to the lexicographic order, and the new $\otimes_2 ... \otimes_{k+2}$ are the piecewise products based 
respectively on 
$\hat{\otimes}_1 ... \hat{\otimes}_{k+1}$ in $\hat{C}.$
\item   
   Even more structure is found in examples 
   with a natural geometric representation which allows
   a use of addition in each product. One such category is that whose objects are Ferrers diagrams,
   by which we mean the shapes
   of Young tableaux. These
   can be presented by a decreasing sequence of nonnegative integers in two ways: the sequence that gives the heights
   of the columns or the sequence that gives the lengths of the rows. We let $\otimes_2$ be the product which
   adds the heights of columns of two tableaux, $\otimes_1$
   adds the length of rows. 
   $$
   A = \xymatrix@W=1.8pc @H=1.8pc @R=0pc @C=0pc @*[F-]{~&~&~&~\\~}
   \text{ and } B = \xymatrix@W=1.8pc @H=1.8pc @R=0pc @C=0pc @*[F-]{~&~\\~\\~}
   $$
   $$
   \text{then } A\otimes_1 B = \xymatrix@W=1.8pc @H=1.8pc @R=0pc @C=0pc @*[F-]{~&~&~&~&~&~\\~&~\\~}
   \text{ and } A\otimes_2 B = \xymatrix@W=1.8pc @H=1.8pc @R=0pc @C=0pc @*[F-]{~&~&~&~\\~&~\\~\\~\\~}
   $$   
   There are several possibilities for morphisms. We can
   create a category equivalent to the non-negative integers in the previous example by pre-ordering the tableaux by height. 
   Here the height $h(A)$ of the tableau is the number of boxes in its leftmost column, and  we say $A \le B$ if $h(A)\le h(B)$. 
   Two tableaux with the same height are isomorphic objects, and the one-column stacks form both a full subcategory and a  skeleton of the category.
   Everything works as for the previous example since $h(A\otimes_2 B) = h(A) +h(B)$ and $h(A\otimes_1 B) = \max(h(A), h(B)).$
   Since we are working with sequences there are also inherited max products as dicussed in the first example.
   The new max with respect to the height preordering is defined as $\max(A,B) = A$ if $B\le A$ and $ = B$ otherwise.
   The piecewise application of max with respect to the ordering of natural numbers results in taking a union
   of the two tableau shapes. 
   Above, $\max(A,B) = B$ and the piecewise max becomes
   $$
   \xymatrix@W=1.8pc @H=1.8pc @R=0pc @C=0pc @*[F-]{~&~&~&~\\~\\~}
   $$
   Both of these latter products are equivalent to the horizontal composition $\otimes_1.$
\item   
Alternatively we can work with the totally ordered structure of the 
tableau shapes given by lexicographic ordering. 
For now we consider the presentation in terms of a monotone decreasing sequence of columns, and regard
an empty column as a height zero column. Every tableau $A$ considered
as an infinite sequence has all zero height columns after some finite natural number $l(A)$. 
Now there are four distinct products, including max with respect to the lexicographic order and piecewise max.
The overall max is thus $\otimes_1.$ Piecewise max is
$\otimes_2.$ Horizontal addition is $\otimes 3$ and vertical addition is 
piecewise addition and will be $\otimes_4.$ By previous discussion
then the tableau shapes with $\otimes_1, \otimes_3, \otimes_4$ form a 3-fold monoidal category.
To see that with $\otimes_2$ this is a valid 4-fold monoidal category  
we need to check first 
that horizontal composition is functorial with respect to the morphisms defined as the $\le$ relations 
of the ordering.  
Note that the horizontal product of tableau shapes $A$ and $C$ can be described as
a reorganization of all the columns of both $A$ and $C$ into a new tableau shape made up of those columns in
 descending order of height. 
 We'll call this sorting.  The cases where
 $A=B$ or $C=D$ are easy. For example let $A_k = B_k$ for all $k$ and
$C_k = D_k$ for all $k < n_{CD}$ Thus the columns from the copies of, for instance $A$ in $A\otimes_1 C$ and 
$A\otimes_1 D$ fall into the same final spot under the sortings right up to the critical location, so
if $C \le D$, then $A\otimes_1 C \le A\otimes_1 D.$
Similarly, it is clear that $A \le B$ implies $(A \otimes_1 D) \le (B \otimes_1 D).$ 
Hence if $A\le B$ and $C\le D$, then
        $A\otimes_1 C \le A\otimes_1 D \le B\otimes_1 D$ which by transitivity gives us our desired property. 




%Now then we assume strict inequalities $A < B$ and $C<D$ 
%and observe the process of creating $A\otimes_1 C $ and $ A\otimes_1 D$ step by step. First put in descending order
%all columns $A_k $ for $k \le n_{AB}$ and $C_j $ for  $j \le n_{CD}.$ We have a sequence of numbers that is precisely
%the same as the descending order listing of all columns $B_k$ for $k \le n_{AB}$ and
%$D_k$ for $k \le n_{CD}.$ Now we consider the next step, of inserting the next columns from our tableau
% shapes into their respective products. We are putting $A_{n_{AB}}$ and $C_{n_{CD}}$ into their
% ordered locations in the descending sequence constructed thus far,
% and putting $B_{n_{AB}}$ and $D_{n_{CD}}$ into an identical sequence. Let $x=\max(A_{n_{AB}},C_{n_{CD}})$
% and $y=\max(B_{n_{AB}},D_{n_{CD}}).$ Then since $A_{n_{AB}} <B_{n_{AB}}$ and $C_{n_{CD}} < D_{n_{CD}}$
% we have that $x<y$. Thus $y$ will be inserted into our sequence of columns at a location closer to
% the beginning than will $x.$ Therefore since $y$ is inserted at a location where it is strictly greater than the 
% entry it is inserted imediately prior to, $y$ will also be strictly greater than the corresponding term in the identical sequence 
% into which we inserted $x.$ Here is a quick explanatory diagram where the blanks represent the two identical sequences.
% 
% $$
%\xymatrix@R=9pt{
%\_\ar@{=}[d]&\_\ar@{=}[dr]&\_\ar@{=}[dr]&x&\_\ar@{=}[d]&\_\ar@{=}[d]&\_\ar@{=}[d]\\
%\_&y\ar@{}[u]|{\Lambda}\ar@{}[r]|{>}&\_&\_&\_&\_&\_
%}
%$$
%
%We conclude that
%$A\otimes_1 C \le B\otimes_1 D$ since the remaining work to be done in constructing the products consists of inserting 
%column height values that will always be smaller than $x$ and $y$ respectively and so will not affect the critical
%location.
 
 Next we check that our interchange transformations will always exist. $\eta^{1j}$ exists by
 the proof of Theorem~\ref{semi} for $j=2,3,4$ since the higher operation all operate on morphisms and
 are thus ordered semigroup operations. We need to check for existence of $\eta^{23}, \eta^{24}, and eta^{34}.$
 
 First for existence of $\eta^{23}$ we need to show that
   $(A \otimes_3 B)\otimes_2(C \otimes_3 D) \le (A \otimes_2 C)\otimes_3 (B \otimes_2 D).$
      We actually show more generally that for any two sequences $a$ and $b$ that 
   $\max_{piecewise}(\sort(a),\sort(b)) \le \sort(\max_{piecewise}(a,b)).$
where we are sorting greater to smaller and taking piecewise maximums. 
To prove the original question we make the two sequences by letting $a$ be $A$ followed by 
$C$ and letting $b$ be $B$ followed by $D$. By followed by we mean padded by zeroes so that
piecewise addition of $a$ and $b$ results in piecewise addition of $A$ and $B$, and respectively $C$ and $D.$

Consider the right hand side of the inequality, where we start with the two sequences and take the 
piecewise maximum of the corresponding pairs of elements before sorting. We can metamorphose this
into the left hand side in stages by using an algorithm to sort $a$ and $b$. Note that if $a$ and $b$ are
already sorted, the inequality becomes an equality.
For our algorithm we choose parallel bubble sorts. These consist
of a series of passes through the sequences comparing $a_n$ and $a_{n+1}$ and  comparing $b_n$ and $b_{n+1}$
simultaneously. If the two elements of a given sequence are not already in decreasing order we 
switch their places. We claim that such an operation always results in a lexicographically smaller
sequence after taking piecewise max and sorting. If both the elements of $a$ and of $b$ are switched, or if neither,
then the result is unaltered. Therefore without loss of generality we assume that $a_n < a_{n+1}$
and that $b_{n+1} \le b_n.$ Then we compare the original
result of sorting after taking the piecewise max and the same but after the switching of $a_n$ and
$a_{n+1}.$ If $b_n \le a_n$ and $b_{n+1} \le a_{n+1}$ then 
$\max(a_n,b_n) = \max(a_n, b_{n+1})$ and $\max(a_{n+1}, b_{n+1}) = \max(a_{n+1}, b_n).$ If $a_n \le b_n$ 
and $a_{n+1} \le b_{n+1}$  then
$\max(a_n,b_n) = \max(a_{n+1}, b_n)$ and $\max(a_{n+1}, b_{n+1}) = \max(a_n, b_{n+1}).$
 Since neither of these cases lead to any change in the final result,
 we may assume $a_n \le b_n$ and $b_{n+1} \le a_{n+1}$, and check two sub-cases:
First $a_{n+1} \le b_n$ implies that
$\max(a_n,b_n) = \max(a_{n+1}, b_n)$ and $\max(a_n, b_{n+1}) \le \max(a_{n+1}, b_{n+1}).$ Second $b_n \le a_{n+1}$
implies that $\max(a_n, b_{n+1}) \le max(a_n,b_n)$ and $\max(a_{n+1}, b_{n+1}) = \max(a_{n+1}, b_n).$ 

Thus after taking piecewise max
and sorting the new result is indeed smaller lexicographically. 

Thus since each move of the parallel bubble sort results in a smaller expression  and the moves
eventually result in $(A \otimes_3 B)\otimes_2(C \otimes_3 D)$, we have $(A \otimes_3 B)\otimes_2(C \otimes_3 D) \le (A \otimes_2 C)\otimes_3 (B \otimes_2 D).$  
  
Secondly the existence of $\eta^{24}$ is clear since the interchange between max and + implies the interchange between 
their piecewise application. Thus we have $(A \otimes_4 B)\otimes_2(C \otimes_4 D) \le (A \otimes_2 C)\otimes_4 (B \otimes_2 D).$
      
   
Finally we need to check that $(A \otimes_4 B)\otimes_3(C \otimes_4 D) \le(A \otimes_3 C)\otimes_4 (B \otimes_3 D).$  
We actually show more generally that for any two sequences $a$ and $b$ of total length
that $Y= \sort(a+b)\le \sort(a)+\sort(b) =X$ where $+$ is the piecewise addition.
To prove the original question we make the two sequences by letting $a$ be $A$ followed by 
$C$ and letting $b$ be $B$ followed by $D$. By followed by we mean padded by zeroes so that
piecewise addition of $a$ and $b$ results in piecewise addition of $A$ and $B$, and respectively $C$ and $D.$
Thus in the original question $l(a) = \max(l(A),l(B)) + l(C) $ and $l(b) = \max(l(A),l(B)) + l(D).$
Recall that $a_k = 0$ for $k>l(a)$.

Consider $Y$, where we start with the two sequences and add them 
piecewise before sorting. We can metamorphose this
into $X$ in stages by using an algorithm to sort $a$ and $b$. Note that if $a$ and $b$ are
already sorted, the inequality becomes an equality.
For our algorithm we choose parallel bubble sorts. These consist
of a series of passes through the sequences comparing $a_n$ and $a_{n+1}$ and  comparing $b_n$ and $b_{n+1}$
simultaneously. If the two elements of a given sequence are not already in decreasing order we 
switch their places. We claim that such an operation always results in a lexicographically smaller
sequence after taking piecewise max and sorting. If both the elements of $a$ and of $b$ are switched, or if neither,
then the result is unaltered. Therefore without loss of generality we assume that $a_n < a_{n+1}$
and that $b_{n+1} < b_n.$ Then we compare the original
result of sorting after taking the piecewise max and the same but after the switching of $a_n$ and
$a_{n+1}.$ It is simplest to note that the new result includes $a_{n+1} + b_n,$ which is larger than
both $a_n + b_n$ and $a_{n+1} + b_{n+1}.$ 

Thus after taking piecewise max
and sorting the new result is indeed larger lexicographically. 

Thus since each move of the parallel bubble sort results in a larger expression  and the moves
eventually result in $(A \otimes_3 C)\otimes_4 (B \otimes_3 D)$, we have $(A \otimes_4 B)\otimes_3(C \otimes_4 D) \le(A \otimes_3 C)\otimes_4 (B \otimes_3 D).$

%We use strong induction on total length. The inequality is trivially true for total length of 1. 
%For a total length of $n+1$ we note the 
%greatest pair of numbers which are in the same location in $\sort(a)$ and $\sort(b)$ but are in location $a_i$
%and $b_j$, $i \ne j$, respectively in $a$ and $b$. Without loss of generality we assume $i>j$ and form 
%$b' = b_1,\dots,b_{j-1},\hat{b_j},\dots,\hat{b_{i-1}},b_i,\dots,b_{l(b)},0\dots$
%by deleting entries $b_j ... b_{i-1}$ from $b.$
%Then let $X' = \sort(a)+\sort(b')$ and $Y' = \sort(a+b').$ By construction $X'<X$ and $Y'>Y.$ By induction
%since $l(a)+l(b') = n+1 - (i-j) \le n$ then $Y' \le X'.$ So $Y<Y'\le X'<X$ and we have the required inequality. 


% Consider the results of these two operations, letting
%   $X=(A \otimes_2 B)\otimes_1(C \otimes_2 D)$
% and $Y(A \otimes_1 C)\otimes_2 (B \otimes_1 D).$ Assume that $Y<X.$ Then $Y_k = X_k$ for $k<n=n_{YX}$ and $Y_n < X_n.$
% For $k<n$ let $Y_k = X_k = p_k + q_k$ where $p_k$ is the height of a column in $A$ or $C$ and $q_k$ is the height of a column
% in $B$ or $D.$ Then $Y_n = y+y'$ where $y = \max\{A\bigcup C - \{p_k\}_{k=1}^{n-1}\}$, the 
% largest column in $A$ or $C$ excepting the columns $p_k,$ and $y' = \max\{B\bigcup D-\{q_k\}_{k=1}^{n-1}\},$ the 
% largest column in $B$ or $D$ excepting the columns $q_k.$
% Now $X_n = x + x'$ for some pair $x,x'$ where $x$ is the height of a column in $A$ or $C$ excepting the columns $p_k$ 
% and $x'$ is the height of a column
% in $B$ or $D$ excepting the columns $q_k.$ We have that either $y<x$ or $y'<x'$ since $Y_n < X_n.$ But this 
% contradicts the fact that $y$ and $y'$ both are maximal. Therefore $(A \otimes_2 B)\otimes_1(C \otimes_2 D) \le 
% (A \otimes_1 C)\otimes_2 (B \otimes_1 D)$.




\item
 We can start with any totally ordered semigroup $\{G,\le, +\}$ such that the identity
0 is less than any other element and such that $g>h$ implies $g+k > h+k, k+g> k+h.$
We create a 4-fold monoidal category ModSeq$(G)$ with objects monotone decreasing 
finitely non-zero sequences of elements of $G$ and morphisms given by the lexicographic ordering. 
The products are as described for natural number in the previous example.  The common unit is the zero sequence.   
The proofs we have given in 
the previous example for $G = ${\bf N} are all still valid.Notice that in the last two proofs, the 
product of two sequences given by sorting their elements
behaves differently with respect to piecewise max and piecewise +. In general for a category of decreasing sequences
the sorting given by $\otimes_k$ will have an interchange with a piecewise operation ${(A\otimes_j B)}_n = A_n*B_n, j < k$
if $ A_n \le B_n $ 
implies $A_n*B_n = B_n.$ Also $\otimes_k$ will have an interchange with a  piecewise operation ${(A\otimes_j B)}_n = A_n*B_n, j > k$
if $ A_n > B_n $ 
implies $A_n*C_n > B_n*C_n.$
This is important when attempting to
 iterate the construction. The objects of ModSeq($G$), sequences under lexicographic order,
 form 4 totally ordered semigroups
using each of the products respectively as the group operation. Thus we can form
2-fold monoidal categories based on any of these semigroup structures. Instead of 
the expected 6-fold category, however, we must choose between two possible a 5-fold monoidal categories
 of decreasing sequences (of decreasing sequences).
The reason is that the product given by sorting two sequences of sequences by lexicographic order of their element sequences
does not interchange at all with the product given by taking piecewise( piecewise max). Either of these however,
along with lexicographic sequence max, piecewise lexicographic max, piecewise sorting, and piecewise (piecewise addition),
do form 5-fold monoidal categories.

% The iteration continues. In general, if we have a $k$-fold monoidal category $C$ with ordering of objects and the
%common unit $I$ such that $A\in C \Rightarrow I\le A,$
% we can form the $(k+2)$-fold monoidal ModSeq$(C)$ with objects ordered lexicographically. 
%$\otimes_1$ and $\otimes_2$ are the is the recombining of sequences with
%respect to the underlying order, and $\otimes'_2 ... \otimes'_{k+1}$ are the component-wise products based 
%respectively on 
%$\otimes_1 ... \otimes_k$ in $C.$


It might be nice to retain the geometric picture of the products of tableau shapes in terms of vertical
and horizontal addition, and addition in other directions as dimension increases. This is not found
in the current version of iteration.
For instance if ModSeq({\bf N}) is our category of tableau shapes
then ModSeq(ModSeq({\bf N})) has objects monotone decreasing sequences of tableau, which we can visualize along the
$z$-axis. For example, if:
$$
A=\xymatrix @W=1.0pc @H=1.0pc @R=1.0pc @C=1.0pc
 {*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}\ar@{-}[r]&*=0{}
\\
*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}\ar@{-}[r]&*=0{}
\\
*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\
*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}}
\text{ and }B=\xymatrix @W=1.0pc @H=1.0pc @R=1.0pc @C=1.0pc
 {*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}}
$$
then $A\otimes_1 B = A$, $A\otimes_2 B = A$ and 
$$
A \otimes_3 B=\xymatrix @W=1.0pc @H=1.0pc @R=1.0pc @C=1.0pc
 {*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}}
A \otimes_4 B=\xymatrix @W=1.0pc @H=1.0pc @R=1.0pc @C=1.0pc
  {*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}}
$$
and
$$
A \otimes_5 B=\xymatrix @W=1.0pc @H=1.0pc @R=1.0pc @C=1.0pc
 {*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}}
$$
The ``addition'' point of view is restored
if we restrict to sequences of tableau shapes that are decreasing in columns as well as rows.
These are lexicographically decreasing sequences of decreasing sequences so already obey the requirement that
${A_n}_1$ is decreasing in $n$. We expand this to require that ${A_n}_k$ be decreasing in $n$ for constant $k$,
which implies decreasing in $k$ for constant $n.$
Then we define a product for which $((A\otimes B)_n)_k = (/sort({A_i}_k,{B_i}_k)_{i=1}^{l(A)+l(B)})_n.$ 
For example, if:
$$
A=\xymatrix @W=1.0pc @H=1.0pc @R=1.0pc @C=1.0pc
 {*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}\ar@{-}[r]&*=0{}
\\
*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}\ar@{-}[r]&*=0{}
\\
*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}\ar@{-}[r]&*=0{}
\\
*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}}
\text{ and }B=\xymatrix @W=1.0pc @H=1.0pc @R=1.0pc @C=1.0pc
 {*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
\\*=0{}&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
\\*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}}
$$
then we let
$$
A \otimes_1 B=\xymatrix @W=1.0pc @H=1.0pc @R=1.0pc @C=1.0pc
 {*=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
 \\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
 \\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
 \\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
 \\*=0{}\ar@{-}[r]&*=0{}
 \\
 *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
 \\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}
 \\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
 \\*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
 \\*=0{}\ar@{-}[r]&*=0{}
 \\
 *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
 \\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
 \\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
 \\*=0{}&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]&*=0{}
  \\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]&*=0{}&*=0{}
  \\*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
  \\*=0{}&*=0{}\ar@{-}[r]&*=0{}
  \\
    *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]&*=0{}
  \\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}
  \\*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
  \\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}&*=0{}
\\
  *=0{}&*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[r]\ar@{-}[dl]&*=0{}\ar@{-}[dl]
  \\*=0{}&*=0{}&*=0{}&*=0{}\ar@{-}[r]&*=0{}\ar@{-}[r]&*=0{}
\\*=0{}}
$$
\end{enumerate}


   
\newpage   
\MySection{$n$-fold operads}    
      Let ${\cal V}$ be an $n$-fold monoidal category as defined in the previous section.
      \begin{definition}
      An operad ${\cal C}$ in ${\cal V}$ consists of objects ${\cal C}(j)$, $j\ge 1$, 
      a unit map ${\cal J}:I\to {\cal C}(1)$, 
      %a right action by the symmetric group
      %$\Sigma_j$ on ${\cal C}(j)$ for each $j$ 
      and composition maps in ${\cal V}$
      $$
      \gamma:{\cal C}(k) \otimes_1 {\cal C}(j_1) \otimes_2 \dots \otimes_2 {\cal C}(j_k)\to {\cal C}(j)
      $$
      for $k\ge 1$, $j_s\ge0$ for $s=1\dots k$ and $\sum\limits_{n=1}^k j_n = j$. The composition maps obey the following axioms
      \begin{enumerate}
      \item Associativity: The following diagram is required to commute for all $k\ge 1$, $j_s\ge 0$ and $i_t\ge 0$, and
      where $\sum\limits_{s=1}^k j_s = j$ and $\sum\limits_{t=1}^j i_t = i.$ Let $g_s= \sum\limits_{n=1}^s j_n$ and
      let $h_s=\sum\limits_{n=1+g_{s-1}}^{g_s} i_n$.

      $$
      \xymatrix{
      {\cal C}(k)\otimes_1\left(\bigotimes\limits_{s=1}^k{}_2 {\cal C}(j_s)\right)\otimes_1\left(\bigotimes\limits_{r=1}^j{}_2 {\cal C}(i_r)\right)
      \ar[rr]^>>>>>>>>>>>>{\gamma \otimes_1 \text{id}}
      \ar[dd]_{\text{id} \otimes_1 \eta^{12}}
      &&{\cal C}(j)\otimes_1 \left(\bigotimes\limits_{r=1}^j{}_2 {\cal C}(i_r)\right)
      \ar[d]^{\gamma}
      \\
      &&{\cal C}(i)
      \\
      {\cal C}(k)\otimes_1 \left(\bigotimes\limits_{s=1}^k{}_2 {\cal C}(j_s)\otimes_1\left(\bigotimes\limits_{q=1}^{j_s}{}_2 {\cal C}(i_{q+g_{s-1}})\right)\right)
      \ar[rr]_>>>>>>>>>>{\text{id} \otimes_1(\otimes^k_2\gamma)}
      &&{\cal C}(k)\otimes_1\left(\bigotimes\limits_{s=1}^k{}_2 {\cal C}(h_s)\right)
      \ar[u]_{\gamma}
      }
      $$
      \end{enumerate}
     Respect of units is required just as in the symmetric case.
          The following unit diagrams commute.
      $$
      \xymatrix{
      {\cal C}(k)\otimes_1 (\otimes_2^k I)
      \ar[d]_{1\otimes_1(\otimes_2^k \eta)}
      \ar@{=}[r]^{}
      &{\cal C}(k)\\
      {\cal C}(k)\otimes_1(\otimes_2^k {\cal C}(1))
      \ar[ur]_{\gamma}
      }
      \xymatrix{
      I\otimes_1 {\cal C}(k)
      \ar[d]_{\eta\otimes_1 1}
      \ar@{=}[r]^{}
      &{\cal C}(k)\\
      {\cal C}(1)\otimes_1 {\cal C}(k)
      \ar[ur]^{\gamma}
      }
      $$
      \end{definition}
      
      \begin{example}
      ~
      \end{example}
      One large family of operads in ModSeq({\bf N}) is that of natural number indexed collections of tableau shapes
       ${\cal C}(n), n\in${\bf N}, such that
      $h({\cal C}(n)) = f(n)$ where $f:${\bf N}$\to${\bf N} is a function such 
      that $f(1) = 0$ and $f(i+j)\ge f(i) + f(j).$
      These conditions are not necessary, but they are sufficient since they imply that ${\cal C}(n) =0$ which shows the
      unit conditions are satisfied and that 
      $h({\cal C}(k)\otimes_1({\cal C}(j_1)\otimes_2...\otimes_2{\cal C}(j_k))) =
       \max(f(k), \sum{f(j_i)}) \le f(j) =h({\cal C}(j))$ which shows that the maps $\gamma$ exist. 
      

      
      Examples of $f$ include  $(x-1)P(x)$ where $P$ is a polynomial with coefficients in {\bf N}. This is easy to show
      since then $P$ will be monotone increasing for 
      $x\ge 1$ and thus $(i+j-1)P(i+j) = (i-1)P(i+j)+jP(i+j) \ge (i-1)P(i)+jP(j) - P(j).$
      By this argument we can also use any $f= (x-1)g(x)$ where $g:${\bf N}$\to${\bf N} is monotone  increasing 
      for $x \ge 1.$
      
      For a specific example with a 
      handy picture that also illustrates again the nontrivial use of the interchange $\eta$
      we simply let $f = x-1.$ Then we have to actually describe the elements of ModSeq({\bf N}) that make up the
      operad. One nice choice is the operad ${\cal C}$ where ${\cal C}(n) = \{n-1,n-1,...,n-1\},$ the  
      $(n-1)\times (n-1)$ square tableau shape. 
      
      ${\cal C}(1) = 0$, ${\cal C}(2) = \xymatrix@W=1.2pc @H=1.2pc @R=0pc @C=0pc @*[F-]{~}$, 
      ${\cal C}(3) = \xymatrix@W=1.2pc @H=1.2pc @R=0pc @C=0pc @*[F-]{~&~\\~&~} \dots$
      
      For instance $\gamma:{\cal C}(3)\otimes_1 ({\cal C}(1)\otimes_2{\cal C}(3)\otimes_2{\cal C}(2)) \to {\cal C}(6)$
      appears as the relation
      $$
      \xymatrix@W=1.2pc @H=1.2pc @R=0pc @C=0pc @*[F-]{~&~&~&~\\~&~&~&~\\~} \le \xymatrix@W=1.2pc @H=1.2pc @R=0pc @C=0pc @*[F-]{~&~&~&~&~\\~&~&~&~&~\\~&~&~&~&~\\~&~&~&~&~\\~&~&~&~&~}
      $$
      An instance of the associativity diagram with upper left position 
      ${\cal C}(2)\otimes_1({\cal C}(3)\otimes_2{\cal C}(2))\otimes_1
      ({\cal C}(2)\otimes_2{\cal C}(2)\otimes_2{\cal C}(4)\otimes_2{\cal C}(5)\otimes_2{\cal C}(3))$ is as follows:
      
      \begin{tabular}{lll}
      $\xymatrix@W=.7pc @H=.7pc @R=0pc @C=0pc @*[F-]{~&~&~&~&~&~&~\\~&~&~&~&~&~\\~&~&~&~&~\\~&~&~&~\\~&~&~\\~&~&~\\~&~&~\\~&~\\~&~\\~\\~}$&$\to$&$\xymatrix@W=.7pc @H=.7pc @R=0pc @C=0pc @*[F-]{~&~&~&~&~&~&~&~\\~&~&~&~&~&~&~&~\\~&~&~&~&~&~&~&~\\~&~&~&~&~&~&~&~\\~&~&~\\~&~&~\\~&~&~\\~&~\\~&~\\~\\~}$ \\
      &&$\downarrow$\\
      $\downarrow$&&$\xymatrix@W=1.7pc @H=1.7pc @R=0pc @C=0pc @*[F-]{15\times 15 \text{ square }}$\\
      &&$\uparrow$\\
      $\xymatrix@W=.7pc @H=.7pc @R=0pc @C=0pc @*[F-]{~&~&~&~&~&~\\~&~&~&~&~\\~&~&~&~&~\\~&~&~&~\\~&~&~&~\\~&~&~&~\\~&~&~\\~&~\\~&~\\~\\~}$&$\to$&$\xymatrix@W=.7pc @H=.7pc @R=0pc @C=0pc @*[F-]{~&~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~\\~&~&~&~&~&~&~}$\\
      \end{tabular}

      

\begin{definition}\label{opalg}
      Let ${\cal C}$ be an n-fold operad.
      \end{definition}
      
      The product of
      two operads is given by
      $$({\cal C}\otimes^{(1)}_i {\cal D})(j) = {\cal C}(j) \otimes_{i+2} {\cal D}(j).$$
      If $A$ is an algebra of ${\cal C}$ and $B$ is an algebra of ${\cal D}$ then, for example,
      $A\otimes_3 B$ is an algebra for ${\cal C}\otimes^{(1)}_1{\cal D}.$
    
      
   %{bib2}
      
      
      
      
      
      
       
        % {bib}
        
        %\clearpage
        \newpage
        \refs
        %\bibitem[Baez and Dolan, 1998]{Baez1}{J. C. Baez and J. Dolan, Categorification, in ``Higher Category Theory'', 
        %eds. E. Getzler and M. Kapranov, Contemp. Math. 230 , American Mathematical Society, 1-36, (1998).}
        \bibitem[Balteanu et.al, 2003]{Balt}{C. Balteanu, Z. Fiedorowicz, R. Schw${\rm \ddot a}$nzl, R. Vogt, 
        Iterated Monoidal Categories,
        Adv. Math. 176 (2003), 277-349.}
        \bibitem[Borceux, 1994]{Borc}{F. Borceux, Handbook of Categorical Algebra 1: 
        Basic Category Theory, Cambridge University Press, 1994.}
        %\bibitem[Day, 1970]{Day}{B.J. Day, On closed categories of functors, Lecture Notes in 
        %Math 137 (Springer, 1970) 1-38}
        %\bibitem[Eilenberg and Kelly, 1965]{EK1}{S. Eilenberg and G. M. Kelly, Closed Categories, 
        %Proc. Conf. on Categorical Algebra, 
        %Springer-Verlag (1965), 421-562. }
        \bibitem[Forcey, 2004]{forcey1}{S. Forcey, Enrichment Over Iterated Monoidal Categories,
        Algebraic and Geometric Topology 4 (2004), 95-119.}
       %\bibitem[Forcey, 2003]
       %{forcey2}{S. Forcey, Higher Dimensional Enrichment, preprint math.CT/0306086, 2003.}
        \bibitem[Kelly, 1982]{Kelly}{G. M. Kelly, Basic Concepts of Enriched Category Theory, London Math. 
        Society Lecture Note Series 64, 1982.}
        \bibitem[Litvinov and Sobolevskii, 2001]{LitSob}{G. Litvinov and A. Sobolevskii, Idempotent 
        Interval Analysis and Optimization Problems, Reliable Computing, vol. 7, no. 5 (2001), 353-377.}
       % \bibitem[Lyubashenko, 2003]{Lyub}{V. Lyubashenko, Category of $A_{\infty}$-categories, 
       % Homology, Homotopy and Applications 5(1) (2003), 1-48.}
        \bibitem[Mac Lane, 1998]{MacLane}{S. Mac Lane, Categories for the 
        Working Mathematician 2nd. edition, Grad. Texts in Math. 5, 1998.}
        \bibitem[Schr\"{o}der, 2003]{Schrod}{Bernd S.W. Schr\"{o}der, Ordered Sets, an Introduction, Birkh\"{a}user, 2003.} 
        \bibitem[Speyer and Sturmfels, 2004]{Sturm}{D. Speyer and B. Sturmfels, Tropical Mathematics, preprint math.CO/0408099, 2004.}
      \endrefs
    
\end{document}
